Articles of Association of London Hackspace Ltd.

### 2011-07-25 constitution/articles-body.tex
Remove definition ambiguity

\item
  In the articles:
  \begin{description}
  \item[Address] means a postal address or, for the purposes of
    electronic communication, a fax number, an e-mail or postal address
    or a telephone number for receiving text messages in each case
    registered with the charity
  \item[The Articles] means the charity's articles of association
  \item[The Charity] means the company intended to be regulated by the
    articles
  \item[Clear days] in relation to the period of a notice means a period
    excluding:
    \begin{itemize}
    \item
      the day when the notice is given or deemed to be given; and
    \item
      the day for which it is given or on which it is to take effect
    \end{itemize}
  \item[The Commission] means the Charity Commission for England and Wales
  \item[Companies Acts] means the Companies Acts (as defined in section
    2 of the Companies Act 2006) insofar as they apply to the charity
  \item[The Directors] means the directors of the charity. The directors
    are charity trustees as defined by section 97 of the Charities Act
    1993
  \item[Document] includes, unless otherwise specified, any document
    sent or supplied in electronic form
  \item[Electronic Form] has the meaning given in section 1168 of the Companies Act 2006
  \item[The Memorandum] means the charity's memorandum of association
  \item[Officers] includes the directors and the secretary (if any)
  \item[The seal] means the common seal of the charity if it has one
  \item[Secretary] means any person appointed to perform the duties of
    the secretary of the charity
  \item[The United Kingdom] means Great Britain and Northern Ireland.
  \end{description}
  Words importing one gender shall include all genders, and the singular
  includes the plural and vice versa.

>>>>

\item
  In the articles:
  \begin{description}
  \item[Address] means a postal address or, for the purposes of
    electronic communication, a fax number, an e-mail or postal address
    or a telephone number for receiving text messages in each case
    registered with the charity
  \item[The Articles] means these articles of association
  \item[Clear days] in relation to the period of a notice means a period
    excluding:
    \begin{itemize}
    \item
      the day when the notice is given or deemed to be given; and
    \item
      the day for which it is given or on which it is to take effect
    \end{itemize}
  \item[The Commission] means the Charity Commission for England and Wales
  \item[Companies Acts] means the Companies Acts (as defined in section
    2 of the Companies Act 2006) insofar as they apply to the charity
  \item[The Directors] means the directors of the charity. The directors
    are charity trustees as defined by section 97 of the Charities Act
    1993
  \item[Document] includes, unless otherwise specified, any document
    sent or supplied in electronic form
  \item[Electronic Form] has the meaning given in section 1168 of the Companies Act 2006
  \item[Officers] includes the directors and the secretary (if any)
  \item[Secretary] means any person appointed to perform the duties of
    the secretary of the charity
  \end{description}
  Words importing one gender shall include all genders, and the singular
  includes the plural and vice versa.
